### 2023-01-25 paper.Rmd
added URL for OSF repo

The simulation was implemented using the statistical programming language R [Version 4.2, @R-base]. The R package `anticlust` [Version 0.6.1, @R-anticlust; @papenberg2020] was used to optimize the anticlustering objectives. The R package `faux` [Version 1.1.0, @R-faux] was used to generate the multivariate normal data sets that were processed during the simulation. The R packages `dplyr` [Version 1.0.7, @R-dplyr], `ggplot2` [Version 3.3.5, @R-ggplot2], `papaja` [Version 0.1.1.9001, @R-papaja], `tidyr` [Version 1.1.3, @R-tidyr] and `DescTools` [Version 0.99.45, @R-desctools] were used for data analysis and result presentation. The simulation study is fully reproducible via code and data that is accessible from the accompanying OSF repository (**link TODO**).

@@

I used the function `kplus_anticlustering()` to divide the data set of 900 images into 9 groups of 100 images each. The first argument of the function call is a variable named `features`, which contains the image data as a table: 900 rows representing images and 3 columns representing the features beauty, arousal, and valence. The accompanying OSF repository contains the full code to reproduce the example (**TODO**).

>>>>

The simulation was implemented using the statistical programming language R [Version 4.2, @R-base]. The R package `anticlust` [Version 0.6.1, @R-anticlust; @papenberg2020] was used to optimize the anticlustering objectives. The R package `faux` [Version 1.1.0, @R-faux] was used to generate the multivariate normal data sets that were processed during the simulation. The R packages `dplyr` [Version 1.0.7, @R-dplyr], `ggplot2` [Version 3.3.5, @R-ggplot2], `papaja` [Version 0.1.1.9001, @R-papaja], `tidyr` [Version 1.1.3, @R-tidyr] and `DescTools` [Version 0.99.45, @R-desctools] were used for data analysis and result presentation. The simulation study is fully reproducible via code and data that has been made accessible via an accompanying OSF repository [@osf2023].

@@

I used the function `kplus_anticlustering()` to divide the data set of 900 images into 9 groups of 100 images each. The first argument of the function call is a variable named `features`, which contains the image data as a table: 900 rows representing images and 3 columns representing the features beauty, arousal, and valence. The accompanying OSF repository contains the full code to reproduce the example [@osf2023].
